**First high-frequency time series of carbonate chemistry in the Arctic**

### 2022-03-30 awipev-CO2_presentation.Rmd
Two columns

@@

## **Availability of data**
Many challenges:

@@

Nevertheless:
- data usable 50 to 76% of the time during the period of measurement
- pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months

![ ](figures/availability.png){ width=70% }

@@

>>>>

![ ](images/intake.png)

@@

## **Availability of data**
:::: {style="display: flex;"}
::: {class='col-md-4'}
Many challenges:

@@

Nevertheless:

- data usable 50 to 76% of the time during the period of measurement
- pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months
:::
::: {class='col-md-8'}

![ ](figures/availability.png){ width=70% }
:::
::::

## **Total alkalinity vs salinity relationship**
![ ](figures/p_at_s.png)

@@

## **Monthly means**
![ ](figures/ts_boxplots.png)

## **Consistency**
![ ](figures/pco2_calc_meas.png)

## **Water column stratification**
#::: {style="text-align:center" markdown="1"}
  ![ ](figures/deltas.png)
#:::
***
